### 2020-01-25 ChapterImplementation/chapterImplementation.tex
Updated: Individual Server Breakdown subsection

\subsection{Server-Region Topology}
Server-region topologies and how they affect the communication requirements between servers will now be discussed. 
AP allows for the simulation space to be partitioned into any topology. In terms of communication, all servers need to communicate with all of their neighbours in order to satisfy the solution to the corner case, as described in \ref{CornerCase}. We define a neighbour as any server that shares a region boundary, including at a corner.

@@

\subsection{Individual Server Breakdown}
%TODO: Describe diagram

@@

\subsection{Server-created replica objects}
The visualiser supports server-created replica objects, which are limited to pre-defined basic objects (cuboid, sphere \& capsule). A different render material per server is used to identify the owning server of each object. These server objects have pre-defined representations on the client. The server sends an identifier for the type of object, which is then created on the client. Using pre-defined objects means the whole geometry of the object does not need to be transferred to the client. This is useful for when there are a large number of identical objects as it avoids having to re-send the same geometry for each object. However, this method requires the client to know of these pre-defined types.

@@

\subsection{Client-created static objects}
In addition to replica objects, static object can also be created by the client. As these objects are static, there is no need for their states to be replicated as they do not change over the course of the simulation. Static object work simply by the client sending the geometry, position and rotation details of the static object to all servers and the servers then re-create the static object. These static objects then remain unchanged throughout the simulation, requiring no updates to the state to be communicated to the client. Static objects are created on all servers, this could be optimised so only static objects within a server's region are created, however, AP can lead to clusters of objects being simulated outside of their host server's region, which may interact with static objects that do not exist on their host server. In addition, the cost of simulating static objects tends to be very low, as they do not require any updates as they are not dynamic. In the future, region boundaries may change; a server may become responsible for a static object previously residing in another server's region, which would then have to be communicated when the region boundaries changed, by all servers simulating all static objects, this avoids the need for extra communication when server boundaries change. With these trade-offs in mind, we have elected to create all static objects on all servers, when static objects are used in a simulation.

\subsection{Interactivity}
The visualiser also allows for interactivity, the creation of server-created objects can be triggered from the client. This feature uses RakNet's Remote Procedure Calls (RPCs), which enables clients to execute procedures on the server, including any required parameters. The client sends a RPC (triggered by a key press) with the parameters of player position and forward direction. The RPC message is received by all servers, only the server which is responsible for the player position creates a server-created object at that position and the object is given a velocity in the direction of the player's direction. This allows the player to create new objects at run-time, which are then able to interact with all objects in the simulation.

>>>>

\subsection{Server-Region Topology}\label{Topology}
Server-region topologies and how they affect the communication requirements between servers will now be discussed. 
AP allows for the simulation space to be partitioned into any topology. In terms of communication, all servers need to communicate with all of their neighbours in order to satisfy the solution to the corner case, as described in \ref{CornerCase}. We define a neighbour as any server that shares a region boundary, including at a corner.

@@

\subsection{Individual Server Breakdown}
The components that make up an individual server, as illustrated in \ref{fig_stack}, will now be discussed. Each server is connected to the client ($C_1$) and all neighbouring servers $S_1..S_N$ (the definition of neighbouring nodes is discussed in \ref{Topology}). The server connects to both of these types through the RakNet library. RakNet includes the Replica Manager and RPCs used by client.

For each boundary with a neighbouring server, a server has three message buffers 1) A migration buffer for sending objects to the server corresponding with that boundary. Each element in the buffer is a message for one object migration. Each migration message contains all data necessary to reproduce the object on the receiving server. 2) An aura creation/update buffer, each element of the buffer is a message for the creation or update of an aura and includes ID, position and radius of the aura. The contents of this buffer are sent to all neighbouring servers, not just the server corresponding with this boundary. The messages structure for both creation and update are identical as the receiving server creates a new aura if one does not already exist for the corresponding object (determined using the ID), otherwise the message is just used to update the state of the existing aura. 3) An aura delete buffer, each element of the buffer is a message for the deletion of an aura, which consists of the aura's ID. The contents of this buffer are sent to all neighbouring servers, not just the server corresponding with this boundary.

Aura Projection receives and processes the messages received from the neighbouring servers. This includes the creation of migrating objects in the PhysX simulation, the creation and updates of the trigger volumes for auras and the deletion of auras in the PhysX simulation.

PhysX provides callbacks for collision events, such as when an object collides with an object's aura or collides with a trigger boundary aura.

The Replica manager tracks the states of objects that are being replicated and sends changes of state to the client. The Replica manager also receives replica creation messages from the client (as described in \ref{Client-CreatedReplicas})

RPCs allow the client to call procedures on the server, including the creation of server-created replicas (as described in \ref{Server-CreatedReplicas}). RPCs enable the client to interact with the servers through various features described in \ref{Interactivity}

@@

\subsection{Server-created replica objects}\label{Server-CreatedReplicas}
The visualiser supports server-created replica objects, which are limited to pre-defined basic objects (cuboid, sphere \& capsule). A different render material per server is used to identify the owning server of each object. These server objects have pre-defined representations on the client. The server sends an identifier for the type of object, which is then created on the client. Using pre-defined objects means the whole geometry of the object does not need to be transferred to the client. This is useful for when there are a large number of identical objects as it avoids having to re-send the same geometry for each object. However, this method requires the client to know of these pre-defined types.

@@

\subsection{Client-created static objects}\label{Client-CreatedReplicas}
In addition to replica objects, static object can also be created by the client. As these objects are static, there is no need for their states to be replicated as they do not change over the course of the simulation. Static object work simply by the client sending the geometry, position and rotation details of the static object to all servers and the servers then re-create the static object. These static objects then remain unchanged throughout the simulation, requiring no updates to the state to be communicated to the client. Static objects are created on all servers, this could be optimised so only static objects within a server's region are created, however, AP can lead to clusters of objects being simulated outside of their host server's region, which may interact with static objects that do not exist on their host server. In addition, the cost of simulating static objects tends to be very low, as they do not require any updates as they are not dynamic. In the future, region boundaries may change; a server may become responsible for a static object previously residing in another server's region, which would then have to be communicated when the region boundaries changed, by all servers simulating all static objects, this avoids the need for extra communication when server boundaries change. With these trade-offs in mind, we have elected to create all static objects on all servers, when static objects are used in a simulation.

\subsection{Interactivity}\label{Interactivity}
The visualiser also allows for interactivity, the creation of server-created objects can be triggered from the client. This feature uses RakNet's Remote Procedure Calls (RPCs), which enables clients to execute procedures on the server, including any required parameters. The client sends a RPC (triggered by a key press) with the parameters of player position and forward direction. The RPC message is received by all servers, only the server which is responsible for the player position creates a server-created object at that position and the object is given a velocity in the direction of the player's direction. This allows the player to create new objects at run-time, which are then able to interact with all objects in the simulation.
